---
title: "HaDeX Report"
author: ""
date: ""
output:
  html_document:
    theme: united
    highlight: textmate
    toc: true
    toc_float: true
    number_sections: false
    df_print: paged
params:
  dat_params: list()
  dat_summary: data.frame()
  input_info: list()
  components: list()
---

<style type="text/css">
span { 
      display: block;
      max-width: 100%;
      word-wrap: break-word;
    }
</style>


Report generated on `r Sys.time()` using the [HaDeXGUI](http://github.com/hadexversum/HaDeXGUI) R package, interface
to the [HaDeX](http://github.com/hadexversum/HaDeX) package.

Detected input file: `r ifelse(params[["input_info"]][["is_example"]], "none (example file)", params[["input_info"]][["name"]])`.  

MD5 hash of the input file: `r ifelse(params[["input_info"]][["is_example"]], "none (example file)", params[["input_info"]][["hash"]])`.

# Summary

Protein name : `r params[["dat_params"]][["chosen_protein"]]()`

Protein sequence : <span>`r params[["dat_params"]][["protein_sequence"]]()`</span>

Sequence length : `r params[["dat_params"]][["sequence_length"]]()`

```{r echo = FALSE, results = "asis", warning = FALSE, message = FALSE}
knitr::kable(params[["dat_summary"]])
```

```{r, child="man/summary.md"}
```


```{r echo=FALSE, message=FALSE, warning=FALSE, results="asis"}

for (i in seq_along(params[["components"]])) {
  cat(glue::glue("\n<h1> {names(params[['components']])[i]}</h1>"))
  
  component <- params[["components"]][[i]]
  
  if (is.data.frame(component)) print(knitr::kable(component, format = "html")) else print(component)
}

```

# R Session

```{r, echo=FALSE}

pander::pander(sessionInfo())

```
